Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-07 surfaces-write-up/surface-write-up.tex
aaron's second round edits through 2.2

\begin{document}

\begin{abstract}
 	We give bounds on the degree of generation and relations of
	canonical rings of arbitrary $\bq$-divisors
	on projective spaces of all dimensions
	and Hirzebruch surfaces.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} H^0(X, \lfloor dD \rfloor)$.
We study the generators and relations of canonical
rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
When $D$ is a general $\bq$-divisor on any $\bp^m$ or on any Hirzebruch Surface
$\hirz_m$, we give bounds on the generators and relations of
$R(X, D)$. In particular, we give a complete description of the
canonical ring when $X = \bp^m$ and $D$ is any effective
$\bq$-divisor.

In part, this work is motivated by a recent paper by
O'Dorney \cite{dorney:canonical}, which gives similar descriptions
of canonical rings for general $\bq$-divisors on $\bp^1$. This
study also has connections to the papers by Voight--Zureick-Brown 
\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring}
which provide tight bounds on generators and relations
of canonical rings on arbitrary stacky curves.

@@

Another closely related topic is the Hassett-Keel program 
initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
\begin{align*}
	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0}H^0 \left(
	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
	\alpha\delta \rfloor  \right) 
\end{align*}
in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
appear when considering the canonical ring of surfaces of Kodaira dimension 1.
A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
barthHPV:compactComplexSurfaces}, and
their canonical ring are most naturally described in the setting of
$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.

\ssec{Main Results}

In Section \ref{sec:proj} we prove the following two results bounding
the degree of generators and relations of
stacky canoincal rings on $\bp^m$:
\begin{restatable}{thm}{restateeffective}
\label{thm:proj-effective-intro}
Let $D = \sum_{i = 0}^{n} \alpha_i C_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
$\bp^m$, be an effective divisor on $\bp^m$.

Then the canonical ring
\[
	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
\]

\noindent
is generated in degrees at most $\max_{1 \leq i \leq n}{q_i}$ with
relations generated in degrees at most $2 \max_{1 \leq i \leq n}{q_i}$
\end{restatable}

\begin{restatable}{thm}{restateproj}
\label{thm:proj-generators-relations}
Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
Then notate
\[\ell_i = \lcm_{j\ne i}(k_i).\] 
Let
$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
$D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
Then $R_D$ is generated in degrees at most 
\[
	\sum_{i=0}^n \ell_i a_i
\]

@@

\noindent
where $\alpha_i \in \bq$ and $D_i \in \di X$ is an integral codimension 1 closed subscheme of $X$. When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$. For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_i)$
and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ Let $
	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)$
denote the canonical ring associated to the $\bq$ divisor $D$.
\section{Canonical Rings on Projective Space}
\label{sec:proj}
In this section, we bound the degrees of generators and relations for divisors
on $\bp^m$, for all $m \geq 1$ in Theorem ~\ref{thm:proj-effective-intro}. 
The $\bp^1$ case restricts to the results of
\cite{dorney:canonical}. We also give an explicit description of the
generators of the canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}

@@

Write
\begin{align*}
	D = \sum_{i=0}^{n}\alpha_i D_i.
\end{align*}
where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. Let $D_i$ be
Cartier divisors such that $D_i = V(f_i)$.
We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a
basis for degree one rational functions on $\bp^m$.

\begin{prop}
\label{prop:pm-span-and-basis}
The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying

@@

\begin{proof}
By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
~\eqref{align:pm-span} lie in $H^0(\bp^m,dD)$. To complete the proof, it
suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \lfloor dD \rfloor }{m}$
functions satisfying condition ~\eqref{align:pm-basis}. However we know
$h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show
that those functions satisfying condition ~\eqref{align:pm-basis} are
independent. This follows from the assumption that $f_0,\ldots f_n$ form a
basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $
monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor
$ rational functions.
\end{proof}

@@

\noindent
be the best lower approximations of $\alpha$. Then, the
canonical ring
\[
	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
\]

\noindent
has a minimal presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
x^{\vec{v}}}{x_k^{c_i}}$ where $1 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
with $\deg \vec v = c_i$. Furthermore, it has
relations generated by the following two forms:
\begin{enumerate}
	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
\vec{w} \in \mss_j$, there is a relation of the form either
\begin{flalign*}
	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})
	^{g_{\vec{y}}} &(i < h_{i, j} < j) \\
	\text{or} \\
	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}}
	\cdot \prod_{ \vec{z} \in
	\mss_{h_{i, j} + 1}} (F_{k_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}}
	&(i < h_{i, j} < h_{i, j} + 1 < j).
\end{flalign*}
	\item For each $(i, j)$ with
$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
\mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
~\ref{defn:vec-order}) there is a relation of the form
\begin{align*}
	&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
	- F_i^{\vec{y}} F_j^{\vec{z}} \\
\end{align*}

@@

\noindent
so $\frac{c_i}{d_i}$ is the mediant of the rational numbers
$\frac{\deg \vec{y}}{s}, \frac{\deg \vec{z}}{t}$ which both
do not exceed $\alpha$. One of $\frac{\deg \vec{y}}{s},
\frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that
$\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
(see Definition ~\ref{defn:lower-approximation}).

Next we show that $F^{\vec v}_i$ generate all of $R_D$. In the case $m = 1$, O'Dorney \cite[Theorem 6]
{dorney:canonical} demonstrates that each lattice point $(\beta, \gamma) \in
\bz_{\geq 0}^2$ with $\gamma \leq \beta \alpha$ lies in the $\bz_{\geq 0}$ span
of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
some $h \in \{0, \ldots, r\}$. Let $(\beta, \gamma) = \kappa_1
(d_h, c_h) + \kappa_2 (d_{h + 1}, c_{h + 1})$ for $\kappa_1, \kappa_2 \in
\bz_{\geq 0}$. Any element $\frac{u^{\beta}
x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
\begin{align*}
	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_h}}
	{x_k^{c_h}}\right)^{\kappa_1} \left(\frac{u^{d_{h + 1}}}
	{x_k^{c_{h + 1}}}\right)^{\kappa_2} x^{\vec{v}}.
\end{align*}

@@

Next, we show that the relations given in the statement of the theorem generate all relations. 
In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} of 
products of generators in adjacent degrees where $h$
depends on $i$ and $ j$, so we notate $h_{i, j} := h \in \{1, \ldots, r\}$. We 
also have that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
$\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore,
$h_{i, j} \neq i$ and $h_{i, j} \neq j - 1$ by the proof of the analogous 
statement in $bp^1$ given by O'Dorney
\cite[Theorem 6]{dorney:canonical}. This gives the relations
$G_{i, j}^{\vec{v}, \vec{w}}$.

The application of $G_{i, j}^{\vec{v}, \vec{w}}$ can be used
to transform any monomial in the $F_i^{\vec{v}}$'s involving
indices that differ by more than $1$ to a monomial in the $F_i
^{\vec{v}}$'s involving indices that differ by at most $1$.

@@

\begin{rem}
\label{rem:proj-two-points}
Note that we cannot extend this result to the case when
$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
coefficients in the same manner that O'Dorney does for the
$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
in Example ~\ref{eg:hyperplane}, the degrees of generation of the
canonical ring of a general $\bq$-divisor supported on two
hyperplanes cannot be bounded so tightly. The two-point
$\bp^1$ result leverages the fact that $\bp^1$ has two
independent coordinates.
\end{rem}

@@

If $C$ is of degree $\pdeg$, consider the veronese embedding
$\nu_\pdeg^m: \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
so that the image of $C$ is the intersection of 
a hyperplane in $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$ with $\nu_\pdeg^m(\bp^m)$.
Now, note that the ring $R_{\alpha C}$ is isomorphic to the
$\pdeg$ veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} H^0(\bp^m, d \alpha V(x_0))$ and so
the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
restricted to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
Therefore, we can bound the degree of generators and relations of
$R_D$ over $R_{D'}$ by the degree of generators and
relations for $R_C \cong R_H.$
This reduces the case of a hypersurface $C$ to
a hyperplane $H$, completeting the proof by Theorem
~\ref{thm:proj-one-point}.
\end{proof}

>>>>

\begin{document}
\begin{abstract}
 	We give bounds on the degree of generation and relations of
	canonical rings of arbitrary $\bq$-divisors
	on projective spaces of all dimensions
	and Hirzebruch surfaces. We also give an explicit presentation 		and tight bounds on the
	generators and relations of the canonical ring of an effective
	stacky divisor on projective spaces of all dimensions.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
track of indexing.
We study the generators and relations of canonical
rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
When $D$ is a general $\bq$-divisor on $\bp^m$ or
$\hirz_m$, we give bounds on the generators and relations of
$R(X, D)$. In particular, we give a complete description of the
canonical ring when $X = \bp^m$ and $D$ is any effective
$\bq$-divisor.

In part, this work is motivated by a recent paper by
O'Dorney \cite{dorney:canonical}, which gives similar descriptions
of canonical rings for general $\bq$-divisors on $\bp^1$. This
study also has connections to the papers by Voight--Zureick-Brown 
\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring},
which provide tight bounds on generators and relations
of canonical rings on arbitrary stacky curves.

Another closely related topic is the Hassett-Keel program 
initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
\begin{align*}
	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
	\alpha\delta \rfloor  \right) 
\end{align*}
in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
appear when considering the canonical ring of surfaces of Kodaira dimension 1.
A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
barthHPV:compactComplexSurfaces}, and
the canonical rings of elliptic surfaces most naturally described in the setting of
$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.

@@

\ssec{Main Results and Outline}

In Section \ref{sec:proj} we prove the following two results bounding
the degree of generators and relations of
stacky canonical rings on $\bp^m$:
\begin{restatable}{thm}{restateeffective}
\label{thm:proj-effective-intro}
Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
\frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i$ be a hypersurface of
$\bp^m$.

Then the canonical ring
\[
	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
\]

\noindent
is generated in degrees at most $\max_{1 \leq i \leq n}{k_i}$ with
relations generated in degrees at most $2 \max_{1 \leq i \leq n}{k_i}$
\end{restatable}

\begin{restatable}{thm}{restateproj}
\label{thm:proj-generators-relations}
Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
Then notate
\[\ell_i = \lcm_{j\ne i}(k_i).\] 
Let
$f_0, \ldots, f_n$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
$D_i = V(f_i)$ for all $i$, $\deg(f_i) = a_i,$ and $f_0,\ldots, f_m$ are independent linear polynomials. 
Then $R_D$ is generated in degrees at most 
\[
	\sum_{i=0}^n \ell_i a_i
\]

@@

\noindent
where $\alpha_i \in \bq$ and $D_i \in \di X$ is an integral codimension 1 closed subscheme of $X$. When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$. For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_i)$
and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$. Let $
	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
is a graded ring, we denote the $d$th graded component of $R$ by $R_d$.
\section{Canonical Rings on Projective Space}
\label{sec:proj}
In this section, we bound the degrees of generators and relations for divisors
on $\bp^m$, for all $m \geq 1$ in Theorem ~\ref{thm:proj-effective-intro}. 
The $\bp^1$ case restricts to the results of
\cite{dorney:canonical}. We also give an explicit description of the
generators of the canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}

@@

Write
\begin{align*}
	D = \sum_{i=0}^{n}\alpha_i D_i.
\end{align*}
where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. Let $D_i$ be
Cartier divisors such that $D_i = V(f_i)$.
We shall further assume that (possibly after reordering) $f_0,\ldots, f_{m}$ form a
basis for degree one rational functions on $\bp^m$.

\begin{prop}
\label{prop:pm-span-and-basis}
The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i} \in (R_D)_d$ satisfying

@@

\begin{proof}
By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
~\eqref{align:pm-span} lie in $H^0(\bp^m,dD)$. To complete the proof, it
suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \lfloor dD \rfloor }{m}$
functions satisfying condition ~\eqref{align:pm-basis}. However we know
$h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show
that those functions satisfying condition ~\eqref{align:pm-basis} are
independent. This follows from the assumption that $f_0,\ldots f_n$ form a
basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$ of degree degree $\lfloor d \deg D \rfloor $
form a basis of degree $\lfloor d \deg D \rfloor$ rational functions.
\end{proof}

@@

\noindent
be the best lower approximations of $\alpha$. Then, the
canonical ring
\[
	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
\]

\noindent
has a minimal presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
x^{\vec{v}}}{x_k^{c_i}}$ where $1 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
with $\deg \vec v = c_i$. Furthermore, it has
relations generated by the following two classes of elements.
\begin{enumerate}
	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
\vec{w} \in \mss_j$, there is a relation of the form either
\begin{flalign*}
	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})
	^{g_{\vec{y}}} &(i < h_{i, j} < j) \\
	\text{or} \\
	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}}
	\cdot \prod_{ \vec{z} \in
	\mss_{h_{i, j} + 1}} (F_{k_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}}
	&(i < h_{i, j} < h_{i, j} + 1 < j).
\end{flalign*}
	\item For each $(i, j)$ with
$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
\mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
~\ref{defn:vec-order}) there is a relation of the form
\begin{align*}
	&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
	- F_i^{\vec{y}} F_j^{\vec{z}} \\
\end{align*}

@@

\noindent
so $\frac{c_i}{d_i}$ is the mediant of the rational numbers
$\frac{\deg \vec{y}}{s}, \frac{\deg \vec{z}}{t}$ which both
do not exceed $\alpha$. One of $\frac{\deg \vec{y}}{s},
\frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that
$\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
(see Definition ~\ref{defn:lower-approximation}). Therefore, none of the $F_i^{\vec v}$ are redundant.

Next we show that $F^{\vec v}_i$ generate all of $R_D$. In the case $m = 1$, O'Dorney \cite[Theorem 6]
{dorney:canonical} demonstrates that each lattice point $(\beta, \gamma) \in
\bz_{\geq 0}^2$ with $\gamma \leq \beta \alpha$ lies in the $\bz_{\geq 0}$ span
of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
some $h \in \{0, \ldots, r\}$. A similar strategy works in the case $m > 1$. Let $(\beta, \gamma) = \kappa_1
(d_h, c_h) + \kappa_2 (d_{h + 1}, c_{h + 1})$ for $\kappa_1, \kappa_2 \in
\bz_{\geq 0}$. Any element $\frac{u^{\beta}
x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
\begin{align*}
	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_h}}
	{x_k^{c_h}}\right)^{\kappa_1} \left(\frac{u^{d_{h + 1}}}
	{x_k^{c_{h + 1}}}\right)^{\kappa_2} x^{\vec{v}}.
\end{align*}

@@

Next, we show that the relations given in the statement of the theorem generate all relations. 
In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} of 
products of generators in adjacent degrees where $h$
depends on $i$ and $ j$, so we notate $h_{i, j} := h \in \{1, \ldots, r\}$. We 
also have that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
$\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore,
$h_{i, j} \neq i$ and $h_{i, j} \neq j - 1$
as follows from an analogous proof to that given by O'Dorney
\cite[Theorem 6]{dorney:canonical} for the case of
$\bp^1$. This gives the relations
$G_{i, j}^{\vec{v}, \vec{w}}$.

One can use the relations $G_{i, j}^{\vec{v}, \vec{w}}$
to transform any monomial in the $F_i^{\vec{v}}$'s involving
indices that differ by more than $1$ to a monomial in the $F_i
^{\vec{v}}$'s involving indices that differ by at most $1$.

@@

\begin{rem}
\label{rem:proj-two-points}
Note that we cannot extend this result to the case when
$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
coefficients in the same manner that O'Dorney does for the
$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
in Example ~\ref{eg:hyperplane}, the degrees of generation of the
canonical ring of a general $\bq$-divisor supported on two
hyperplanes cannot be bounded so tightly. The two-point
$\bp^1$ result leverages the fact that $\bp^1$ has precisely two
independent coordinates, so that two distinct integral subschemes
cannot be equations of only $m$ of the $m+1$ coordinates.
\end{rem}

@@

If $C$ is of degree $\pdeg$, consider the veronese embedding
$\nu_\pdeg^m: \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
so that the image of $C$ is the intersection of 
a hyperplane in $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$ with $\nu_\pdeg^m(\bp^m)$.
Now, note that the ring $R_{\alpha C}$ is isomorphic to the
$\pdeg$ veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0))$ and so
the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
restricted to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
Therefore, we can bound the degree of generators and relations of
$R_D$ over $R_{D'}$ by the degree of generators and
relations for $R_C \cong R_H.$
This reduces the case of a hypersurface $C$ to
a hyperplane $H$, completeting the proof by Theorem
~\ref{thm:proj-one-point}.
\end{proof}
